Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2019-01-24 Response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Response to Referees]
    {Response to referee comments \\
    and \\
    changes report}
\keywords{}
\subjclass[2010]{}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

First of all, we would like to thank the reviewer for its time and its
careful reading. Its suggestions improve the paper.
\medbreak

@@

Please find here the modifications made to the manuscript
``Quotients of the magmatic operad: lattice structures and convergent
rewrite systems'' submitted to Experimental Mathematics, following
the comments of the reviewer.
\bigbreak

\begin{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
They were obviously obtained through an expert and
heavy use of computer software.
In my humble opinion, when doing so, one should cite carefully what
is being used (language, package, etc), just like articles are cited.
}''
\smallbreak

@@

This precision has been added to the proof of the lemma.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
In the proof of Lemma 1.3.4, refer to a precise Theorem in [Gir16]
}''
\smallbreak

The precise reference has been added.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item ``{\it
  Page 9, is this completion or rewriting systems an operadic avatar of
  Knuth-Bendix procedure ?
}''
\smallbreak

In essence, this is the same thing but the terminology differs from
the context: for term rewriting ystems or word rewriting systems, the
classical terminology in the litterature is ``Knuth-Bendix procedure''
and for linear structures, such  such as polynomial algebras,
noncommutative algebras or operads, the classical terminology is
''Buchberger procedure".
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item ''{\it
A reference for the name "Grassmann formula" would be welcome (page 12)
}''
\smallbreak

A reference has been added.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item ''{\it
In the proof of Prop. 3.2.5, why not use that the composite of a
morphism is a morphism ?
}''
\smallbreak

This is a good remark: we changed the text.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item ''{\it
What are the squared regions (page 17) ? I did not look at the colored
article.
}''
\smallbreak

@@

This was a mistake because, indeed, there are no squared regions. we
change ``squared regions'' by ``dotted edges''.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item ''{\it
Maybe it would be a good idea to add the words in $\{0,2\}$ below the
relations in the large figure of page 19 ?
}''
\smallbreak

The words in correspondence with the trees of the relations have been
written.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
The definition of $z_d$ page 20 needs to be checked (composition index)
}''
\smallbreak

Indeed, you are right, the index was wrong. We changed "d/2" into
"d-1/2".
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
About table of numbers page 23, do you see any interesting patterns ?
possible formulas ? rationality of generating series ?
}''
\smallbreak

It seems that it is not the case. Even with the package gfun on
Maple, we do not see any pattern, formulas, \dots
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
In section 4, the sentence "The reader can check" (repeated 4 times)
is a bit terse. This is certainly feasible by hand. The reader would
appreciate to be given hints of arguments for confluence (no critical
pair ?) and termination. Or maybe there are available software that
can swallow this kind of rewriting system and check that is is closed ?
}''
\smallbreak

We added the "using the Buchberger algorithm for operads" for the first
occurrence of "The reader can check". It is quite easy to run the
algorithm by hand on those examples.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
Question: make a statement about the non-isomorphism (as set-operads
or as k-linear-operads) between the 4 quotients indexed by compositions.
}''
\smallbreak

This is a good suggestion. We have added a small section (4.2.5) to
explain this property.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
For the conjecture of section 4.3, up to which arity was it verified ?
}''
\smallbreak

Until arity 40. We have added this information in the article.
\medbreak

### 2019-01-24 Response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Response to Referees]
    {Response to referee comments \\
    and \\
    changes report}
\keywords{}
\subjclass[2010]{}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

First of all, we would like to thank the reviewer for his time and his
careful reading. His suggestions improve the paper.
\medbreak

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
About table of numbers page 23, do you see any interesting patterns ?
possible formulas ? rationality of generating series ?
}''
\smallbreak

It seems that it is not the case. Even with the package gfun on
Maple, we do not see any pattern, formulas, \dots
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item `` {\it
In section 4, the sentence "The reader can check" (repeated 4 times)
is a bit terse. This is certainly feasible by hand. The reader would
appreciate to be given hints of arguments for confluence (no critical
pair ?) and termination. Or maybe there are available software that
can swallow this kind of rewriting system and check that is is closed ?
}''
\smallbreak

We added the information "using the Buchberger algorithm for operads" for
the first occurrence of "The reader can check". It is quite easy to run
the algorithm by hand on those examples.
\medbreak
